---
title: "README"
author: "Amanpreet Kaur"
date: "Sunday, July 27, 2014"
output: html_document
---
#Overview of App
This document provides the bried description of the shiny app i built namely "Interactive Linear Models"..
This app uses the R library inbuilt dataset mtcars.
Using this app you can create a linear model of any of the variables in mtcars as predictor and miles per gallon as outcome.
This app also shows the plot between miles per gallon and the predictor selected.

#ui.r
```{r}
library(shiny)
library(ggplot2)

# Define UI for random distribution application 
shinyUI(pageWithSidebar(

  # Application title
  headerPanel("Linear Models for mtcars"),

  # Sidebar with controls to select the predictor variables.
  # Note the use of the br()
  # element to introduce extra vertical spacing
  sidebarPanel(
    textInput("outcome", "Outcome:", "Miles per Gallon"),
    radioButtons("variable", "Select the Predictor Variables:",
                 list("Number of Cylinders" = "cyl",
                      "Displacement" = "disp",
                      "Gross Horse Power" = "hp",
                      "Rear Axle Ratio" = "drat",
                      "Weight"="wt",
                      "1/4 Mile Time"="qsec",
                      "V/S"="vs",
                      "Transmission"="am",
                      "Number of front gears"="gear",
                      "Number of carburetors"="carb")),
    br())
,
  # Show a tabset that includes a plot, summary, and table view
  # of the generated model.
  mainPanel(
    tabsetPanel(
      tabPanel("ModelSummary", verbatimTextOutput("summary")),
      tabPanel("Plot", plotOutput("plot"))
    )
  )
))
```
You can select the predictor by pressing the radio button corresponding to the name of predictor.
You can see the summary of model and plot on the R.H.S.

#server.R
```{r}
library(shiny)
library(ggplot2)
library(datasets)
# Define server logic for random distribution application
shinyServer(function(input, output) {

   # Generate a summary of the data
  output$summary <- renderPrint({
     if (input$variable == "am") {
       fit<-lm(mpg ~ am,data=mtcars)
     }
     else if(input$variable=="disp"){
       fit<-lm(mpg ~ disp,data=mtcars)
     }
    else if(input$variable=="hp"){
      fit<-lm(mpg ~ hp,data=mtcars)
     }
    else if(input$variable=="drat"){
      fit<-lm(mpg ~ drat,data=mtcars)
     }
    else if(input$variable=="wt"){
      fit<-lm(mpg ~ wt,data=mtcars)
     }
   else if(input$variable=="qsec"){
      fit<-lm(mpg ~ qsec,data=mtcars)
     }
   else if(input$variable=="vs"){
      fit<-lm(mpg ~ vs,data=mtcars)
     }
   else if(input$variable=="cyl"){
      fit<-lm(mpg ~ cyl,data=mtcars)
     }
   else if(input$variable=="gear"){
     fit<-lm(mpg ~ gear,data=mtcars)
     }
   else if(input$variable=="carb"){
      fit<-lm(mpg ~ carb,data=mtcars)
}
    summary(fit)
  })

   # Generate a plot of the data. Also uses the inputs to build the 
  # plot label. Note that the dependencies on both the inputs and
  # the 'data' reactive expression are both tracked, and all expressions 
  # are called in the sequence implied by the dependency graph
  output$plot <- renderPlot({
    if (input$variable == "am") {
       mpgData <- data.frame(mpg = mtcars$mpg, var = factor(mtcars[[input$variable]], labels = c("Automatic", "Manual")))
     }
     else if(input$variable=="disp"){
        mpgData <- data.frame(mpg = mtcars$mpg, var = factor(mtcars[[input$variable]]))
     }
    else if(input$variable=="hp"){
        mpgData <- data.frame(mpg = mtcars$mpg, var = factor(mtcars[[input$variable]]))
     }
    else if(input$variable=="drat"){
      mpgData <- data.frame(mpg = mtcars$mpg, var = factor(mtcars[[input$variable]]))
     }
    else if(input$variable=="wt"){
      mpgData <- data.frame(mpg = mtcars$mpg, var = factor(mtcars[[input$variable]]))
     }
   else if(input$variable=="qsec"){
      mpgData <- data.frame(mpg = mtcars$mpg, var = factor(mtcars[[input$variable]]))
     }
   else if(input$variable=="vs"){
      mpgData <- data.frame(mpg = mtcars$mpg, var = factor(mtcars[[input$variable]]))
     }
   else if(input$variable=="cyl"){
      mpgData <- data.frame(mpg = mtcars$mpg, var = factor(mtcars[[input$variable]]))
     }
   else if(input$variable=="gear"){
      mpgData <- data.frame(mpg = mtcars$mpg, var = factor(mtcars[[input$variable]]))
     }
   else if(input$variable=="carb"){
     mpgData <- data.frame(mpg = mtcars$mpg, var = factor(mtcars[[input$variable]]))
    }
     p <- ggplot() + 
       geom_point(aes(var,mpg),mpgData,color="blue") + 
       xlab(input$variable)+ylab("mpg")
     print(p)
  })


 })
```